---
title: 'Lab 7: Multiple Linear Regression Intro'
author: "Sophia Leiker"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```


## Explore Penguins

Use `GGally::ggpairs()` to create a pairs plot

```{r}
ggpairs(penguins)
```

That's kind of overkill. Let's simplify the variables that we include in our ggpairs plot:

- species
- bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))

```

## Multiple Linear Regression

We are going to try to understand (a bit better) relationships between multiple predictor variables and an outcome which is penguin body mass/

The different predictor variables we're going to try are: 

- species
- flipper length
- sex
- bill depth


### Model 1

Model body mass based on only flipper length and bill depth (bad idea... important variables missing)

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

#Call model by name to return only the coefficients
model_1

#If I want to get more information on the coefficients and model
summary(model_1)

```

If everything else is held constant, we expect that for each 1mm increase in flipper length, penguin body mass is expected to increase by 51.54 g, on average.

Notes: Adjusted R^2 (coefficient of determination) value: 76% of variance of the penguin body mass (dependent variable) is explained by penguin flipper length and bill depth (independent variables) (there is 24% of body mass that is not explained by this model)
Pearsons R --> strength of correlation (which is different!)

Actually -- we think that a model for penguin body mass should contain variables, species, flipper length, and penguin sex. 

```{r}

model_2 <- lm(body_mass_g ~ flipper_length_mm + sex + species, data = penguins)

#Let's check out the coefficients:
model_2

#The reference level would be Adelie and female (as all the other ones were set to 0)
#Interpreting the coefficients for 
#flipper length, Gentoo, and male

# On average we expect a Gentoo penguin to be 836g larger in body mass on average than an Adelie given everything else is the same. 
#On average we expect a male penguin to be 530g larger in body mass on average than a female given everything else is the same.
#On average for every increase in 1 mm in flipper length there would be a 20g increase in body mass given all other constants held the same --> check this

summary(model_2)

```

## Visualize this model

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color=species)) +
  facet_wrap(~sex)

```

## A couple ways to get and report MLR model outcomes

Use broom::tidy() to get model coefficient info in a tidy data frame.

```{r}
penguin_model2_coef <- tidy(model_2)

tidy(model_2)
```

Try to write inline `r` that spits out the coefficient for Gentoo.
`r  penguin_model2_coef$estimate[5]` (output of this is a vector containing an output of every column)

## Look at the model diagnostics

Use the plot() function.

```{r}
plot(model_2)

summary(model_2)
```

## Report the model outputs in a summary table

```{r}
modelsummary(model_2)
```

Use stargazer:

```{r, results = "asis"}
stargazer(model_2, type= "html")

```

